---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![CRAN status](https://www.r-pkg.org/badges/version/gallerywidget)](https://cran.r-project.org/package=gallerywidget)
[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Travis build status](https://travis-ci.org/ijlyttle/gallerywidget.svg?branch=master)](https://travis-ci.org/ijlyttle/gallerywidget)

# gallerywidget

The goal of gallerywidget is to provide you with the means to create a gallery of images, each of which contains a hyperlink, and may contain a title and a subtitle. The inspiration for this gallery tool is taken from Mike Bostock's
[blocks website](https://bl.ocks.org), as well as the [Vega-Lite website](https://vega.github.io/vega-lite).

## Installation

This package is not yet on CRAN; but you can install it from GitHub:

``` r
#install.packages("devtools")
devtools::install_packages("ijlyttle/gallerywidget")
```

## Example

```{r example}
library("gallerywidget")
library("tibble")
```

This package contains a single function, `gallerywidget()`, and a single sample-dataset, `data_htmlwidgets`. 

The `data_htmlwidgets` dataset was built using examples from the [htmlwidgets gallery](http://gallery.htmlwidgets.org):

```{r}
glimpse(data_htmlwidgets)
```

Each row of the dataset is associated with an example in the gallery; the dataset has four columns:

- `href` URL destination of link
- `image` URL for the preview image 
- `title` character string for the title
- `subtitle` character string for the subtitle

The `gallerywidget()` function is used to render the widget:

```{r}
gallerywidget(data_htmlwidgets)
```

------

## Acknowledgements

As mentioned above, this work is inspired by the galleries for from Mike Bostock's
[blocks website](https://bl.ocks.org), as well as the [Vega-Lite website](https://vega.github.io/vega-lite). The css is a mix of the css from both of these sites - I trust that it is cool with all involved that their code is repurposed in this fashion.



